---
title: "Time Series Analysis for costco Data"
author: "Akshay"
date: "18/04/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(forecast)
library(fpp)
library(knitr)
library(quantmod)
library(timeSeries)
library(tseries)
library(xts)
library(zoo)
library(gridExtra)
suppressMessages(library(dplyr))
library(tidyverse)
library(tibbletime)
library(ggfortify)
```



```{r}
#loading the data
costco <- read_csv("COST.csv")
# check for NA values
sum(is.na(costco))
```

## Plotting general time series plot and Chartseries plot as well

```{r}
#Getting close prices for the costco data
summary(costco)
sd(costco$Close)
costco.close <-ts(costco$Close, start = 2005, frequency = 12)
#view(costco.close)
costco.close
#plotting the general time series plot for costco
plot(costco.close,main="costco", sub="Stock Price Variation with respect to Time",
  xlab="Time (in years)", ylab=" Stock Prices (in USD)",col.lab="green", cex.lab=3, type ="l")

?plot
#converting list object to time series object
costco <- ts(costco)
dates <- as.Date("2005-01","%Y/%m") + 0:180
costco <- as.xts(costco, reclass=FALSE, order_by =dates)


#data to train my models upon : 
costco.Close <- ts(costco$Close, start =c(2005,01), end= c(2017,12), frequency = 12)
costco.Close.test <- ts(costco$Close, start =c(2018,01), end= c(2019,12), frequency = 12)
```

```{r}

summary(costco.close)
sd(costco.close)
```


## Lets decompose : the time series

```{r}
costco.Close.de.add = decompose(costco.Close, type = "additive")
costco.Close.de.mul = decompose(costco.Close, type =  "multiplicative")
costco.close.de.add = decompose(costco.close, type = "additive")
costco.close.de.mul = decompose(costco.close, type =  "multiplicative")
plot(costco.Close.de.mul)
plot(costco.close.de.mul)

```


#lets convert time series into log and sqrt transformed serieses
```{r}
costco.close.log = log(costco.close)
costco.close.sqrt = sqrt(costco.close) 
costco.Close.log = log(costco.Close)
costco.Close.sqrt = sqrt(costco.Close) 
costco.close
plot(costco.close)
plot(costco.close.log)
plot(costco.close.sqrt)

```

# lets perform ADF tests on these Time series
```{r}
adf.test(costco.close)
adf.test(costco.close.log)
adf.test(costco.close.sqrt)
```

## Lets us make differenced time series
```{r}
dcostco.close = diff(costco.close, lag=1)
dcostco.close.log = diff(costco.close.log, lag=1)
dcostco.close.sqrt = diff(costco.close.sqrt, lag=1)
```

## Lets us make differenced time series
```{r}
adf.test(dcostco.close )
adf.test(dcostco.close.log) 
adf.test(dcostco.close.sqrt) 
```

## Lets us make differenced 12 time series
```{r}
dcostco.close.sea = diff(costco.close, lag=12)
dcostco.close.log.sea = diff(costco.close.log, lag=12)
dcostco.close.sqrt.sea = diff(costco.close.sqrt, lag=12)
```

```{r}
library(astsa)
acf2(dcostco.close.sea)

(dcostco.close.log.sea) 
dcostco.close.sqrt.sea 
```
#Lets look at ACF and PACF plots
```{r  height = 10, width = 10}
plot(acf(costco.close), main = "ACF plot for costco closing stock Prices")
plot(acf(costco.close.log))
plot(acf(costco.close.sqrt))
plot(pacf(costco.close))
plot(pacf(costco.close.log))
plot(pacf(costco.close.sqrt))

```



# Fitting auto.arima to get the best model
```{r}
costco.Close.auto.arima= auto.arima(costco.Close, trace = TRUE)
#best model ARIMA(1,1,1) with drift i.e. include.drift=TRUE,
# seasonal best model : ARIMA(1,1,1)(0,0,1)[12] with drif 951

costco.Close.log.auto.arima = auto.arima(costco.Close.log, trace = TRUE)
#best model ARIMA(0,1,0),
#seasonal best model : ARIMA(0,1,0)(2,0,0)[12] with drift -463.86

costco.Close.sqrt.auto.arima = auto.arima(costco.Close.sqrt, trace = TRUE)
#best model ARIMA(0,1,0)with drift
#seasonal best model : ARIMA(0,1,0)(0,0,1)[12] with drift = 13.49
```

#making all the above models
```{r}
costco.Close.arima = Arima(costco.Close, order = c(1,1,1), include.drift = TRUE )
costco.Close.arima.s = Arima(costco.Close, order =c(1,1,1),include.drift = TRUE,seasonal = list(order=c(0,0,1)))
costco.Close.log.arima = Arima(costco.Close.log, order = c(0,1,0), include.drift = FALSE )
costco.Close.log.arima.s = Arima(costco.Close.log, order = c(0,1,0), include.drift = TRUE, seasonal = list(order=c(2,0,0)))
costco.Close.sqrt.arima = Arima(costco.Close.sqrt, order = c(0,1,0), include.drift = TRUE )
costco.Close.sqrt.arima.s = Arima(costco.Close.sqrt, order = c(0,1,0), include.drift = TRUE, seasonal = list(order=c(0,0,1)))

```


#lets make interactive Plots for the test data

```{r}
fcostco.Close.arima = forecast(costco.Close.arima, h=24)
fcostco.Close.arima.s = forecast(costco.Close.arima.s, h=24)
fcostco.Close.log.arima = forecast(costco.Close.log.arima, h=24)
fcostco.Close.log.arima.s = forecast(costco.Close.log.arima.s, h=24)
fcostco.Close.sqrt.arima = forecast(costco.Close.sqrt.arima, h=24)
fcostco.Close.sqrt.arima.s = forecast(costco.Close.sqrt.arima.s, h=24)
```

#lets find RMS error on test set

```{r}
#Values to be predicted
original_val <- window(costco.close, start =2018)
rmserr <- function(x,y){
  p =x-y
  r=sum(p^2)
  r = r /length(x)
  r= sqrt(r)
  return (r)
}
(Ecostco.Close.arima <- rmserr(fcostco.Close.arima$mean,original_val ))
(Ecostco.Close.arima.s <- rmserr(fcostco.Close.arima.s$mean,original_val))
(Ecostco.Close.log.arima. <- rmserr(exp(fcostco.Close.log.arima$mean),original_val ))
(Ecostco.Close.log.arima.s <- rmserr(exp(fcostco.Close.log.arima.s$mean),original_val))
(Ecostco.Close.sqrt.arima. <- rmserr((fcostco.Close.sqrt.arima$mean)^2,original_val ))
(Ecostco.Close.sqrt.arima.s <- rmserr((fcostco.Close.sqrt.arima.s$mean)^2,original_val))

```

```{r}
fcostco.Close.log.arima.s$mean <- 2.718^fcostco.Close.log.arima.s$mean
fcostco.Close.log.arima.s$lower <- 2.718^fcostco.Close.log.arima.s$lower
fcostco.Close.log.arima.s$upper <- 2.718^fcostco.Close.log.arima.s$upper
fcostco.Close.log.arima.s$x <- 2.718^fcostco.Close.log.arima.s$x
fcostco.Close.log.arima.s$fitted <- 2.718^fcostco.Close.log.arima.s$fitted

test_forecast(forecast.obj = fcostco.Close.log.arima.s, actual = costco.close, test = costco.Close.test, Xgrid = TRUE, Ygrid = TRUE) %>%
  plotly::layout(legend = list(x = 0.1, y = 0.95), 
                 title = "Comparision of Predicted and Actual Closing Value of 2018 and 19",
                 yaxis = list(linecolor = "rgb(67,67,67)"),
                 xaxis = list(linecolor = "rgb(67,67,67)"))
```


#lets see the parameters for the best model
```{r}
costco.Close.log.arima.s
```


#fitting the best model for time series till 2020 and prediction for 2023
```{r}
costco.close.log = log(costco.close)
costco.close.log.arima.s = Arima(costco.close.log, order = c(0,1,0), include.drift = TRUE, seasonal = list(order=c(0,0,1)))
Fcostco.close.log.arima.s = forecast(costco.close.log.arima.s,h=36)
exp(costco.close.log.arima.s$fitted)
```
```{r}
exp(Fcostco.close.log.arima.s$mean)
exp(Fcostco.close.log.arima.s$lower)
exp(Fcostco.close.log.arima.s$upper)
exp(Fcostco.close.log.arima.s$fitted)
```
```{r}

Fcostco.close.log.arima.s$mean <- 2.718^Fcostco.close.log.arima.s$mean
Fcostco.close.log.arima.s$lower <- 2.718^Fcostco.close.log.arima.s$lower
Fcostco.close.log.arima.s$upper <- 2.718^Fcostco.close.log.arima.s$upper
Fcostco.close.log.arima.s$x <- 2.718^Fcostco.close.log.arima.s$x
Fcostco.close.log.arima.s$fitted <- 2.718^Fcostco.close.log.arima.s$fitted

plot_forecast(Fcostco.close.log.arima.s, title = "Forcasting of Costco Share Closing price for 2020 to 2023", Xtitle = "Year", Ytitle = "Closing Stock Price") 

#%>% 
 # plotly::layout(legend = list(x = 0.1, y = 0.95),
  #               margin=list(l=20, r=20, t=20, b=20),
   #              yaxis = list(linecolor = "rgb(67,67,67)"),
    #             xaxis = list(linecolor = "rgb(67,67,67)"))


```
```{r}
# Validation of the model by the ljung test 

Box.test(Fcostco.close.log.arima.s$residuals, lag =12, type = "Ljung")


```
#
```{r}
# Confedence interval ofthe 

confint(costco.close.log.arima.s)
Fcostco.close.log.arima.s$mean

```