---
title: "Time Series Analysis for Walmart Data"
author: "Akshay"
date: "18/04/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(forecast)
library(fpp)
library(knitr)
library(quantmod)
library(timeSeries)
library(tseries)
library(xts)
library(zoo)
library(gridExtra)
suppressMessages(library(dplyr))
library(tidyverse)
library(tibbletime)
library(ggfortify)
```



```{r}
#loading the data
Walmart <- read_csv("WMT.csv")
# check for NA values
sum(is.na(Walmart))
```

## Plotting general time series plot and Chartseries plot as well

```{r}
#Getting close prices for the walmart data
Walmart.close <-ts(Walmart$Close, start = 2005, frequency = 12)
summary(Walmart)
#view(Walmart.close)
Walmart.close
#plotting the general time series plot for Walmart
plot(Walmart.close,main="WALMART", sub="Stock Price Variation with respect to Time",
  xlab="Time (in years)", ylab=" Stock Prices (in USD)",col.lab="green", cex.lab=3, type ="l")

?plot
#converting list object to time series object
walmart <- ts(Walmart)
dates <- as.Date("2005-01","%Y/%m") + 0:180
walmart <- as.xts(walmart, reclass=FALSE, order_by =dates)


#data to train my models upon : 
Walmart.Close <- ts(Walmart$Close, start =c(2005,01), end= c(2017,12), frequency = 12)
Walmart.Close.test <- ts(Walmart$Close, start =c(2018,01), end= c(2019,12), frequency = 12)

```

```{r}

summary(Walmart.close)
sd(Walmart.close)
```


## Lets decompose : the time series

```{r}
Walmart.Close.de.add = decompose(Walmart.Close, type = "additive")
Walmart.Close.de.mul = decompose(Walmart.Close, type =  "multiplicative")
Walmart.close.de.add = decompose(Walmart.close, type = "additive")
Walmart.close.de.mul = decompose(Walmart.close, type =  "multiplicative")
plot(Walmart.Close.de.mul)
plot(Walmart.close.de.mul)

```


#lets convert time series into log and sqrt transformed serieses
```{r}
Walmart.close.log = log(Walmart.close)
Walmart.close.sqrt = sqrt(Walmart.close) 
Walmart.close
plot(Walmart.close)
plot(Walmart.close.log)
plot(Walmart.close.sqrt)
Walmart.Close.log = log(Walmart.Close)
Walmart.Close.sqrt = sqrt(Walmart.Close) 

```

# lets perform ADF tests on these Time series
```{r}
adf.test(Walmart.close)
adf.test(Walmart.close.log)
adf.test(Walmart.close.sqrt)
```

## Lets us make differenced time series
```{r}
dWalmart.close = diff(Walmart.close, lag=1)
dWalmart.close.log = diff(Walmart.close.log, lag=1)
dWalmart.close.sqrt = diff(Walmart.close.sqrt, lag=1)
```

## Lets us make differenced time series
```{r}
adf.test(dWalmart.close )
adf.test(dWalmart.close.log) 
adf.test(dWalmart.close.sqrt) 
plot(dWalmart.close.log, main = "Differenced logarithmic Walmart stock closing price Time Series")
```

## Lets us make differenced 12 time series
```{r}
dWalmart.close.sea = diff(Walmart.close, lag=12)
dWalmart.close.log.sea = diff(Walmart.close.log, lag=12)
dWalmart.close.sqrt.sea = diff(Walmart.close.sqrt, lag=12)
```

```{r}
library(astsa)
acf2(dWalmart.close.sea)

plot(dWalmart.close.log.sea) 
dWalmart.close.sqrt.sea 
```
#Lets look at ACF and PACF plots
```{r  height = 10, width = 10}
plot(acf(Walmart.close), main = "ACF plot for Walmart closing stock Prices")
plot(acf(Walmart.close.log))
plot(acf(Walmart.close.sqrt))
plot(pacf(Walmart.close))
plot(pacf(Walmart.close.log))
plot(pacf(Walmart.close.sqrt))
plot(acf(dWalmart.close.log), main = "ACF plot for Walmart closing stock Prices")
plot(pacf(dWalmart.close.log), main = "PACF plot for Walmart closing stock Prices")
```



# Fitting auto.arima to get the best model
```{r}
Walmart.Close.auto.arima= auto.arima(Walmart.Close, trace = TRUE)
#best model ARIMA(0,1,0) with drift i.e. include.drift=TRUE,
# seasonal best model : ARIMA(0,1,0)(0,0,1)[12] with drif

Walmart.Close.log.auto.arima = auto.arima(Walmart.Close.log, trace = TRUE)
#best model ARIMA(0,1,0),
#seasonal best model : ARIMA(0,1,0)(0,0,1)[12] with drift -568.5341

Walmart.Close.sqrt.auto.arima = auto.arima(Walmart.Close.sqrt, trace = TRUE)
#best model ARIMA(0,1,0)
#seasonal best model : ARIMA(0,1,0)(0,0,1)[12] with drift 
```

#making all the above models
```{r}
Walmart.Close.arima = Arima(Walmart.Close, order = c(0,1,0), include.drift = TRUE )
Walmart.Close.arima.s = Arima(Walmart.Close, order =c(0,1,0),include.drift = TRUE,seasonal = list(order=c(0,0,1)))
Walmart.Close.log.arima = Arima(Walmart.Close.log, order = c(0,1,0), include.drift = FALSE )
Walmart.Close.log.arima.s = Arima(Walmart.Close.log, order = c(0,1,0), include.drift = TRUE, seasonal = list(order=c(0,0,1)))
Walmart.Close.sqrt.arima = Arima(Walmart.Close.sqrt, order = c(0,1,0), include.drift = FALSE )
Walmart.Close.sqrt.arima.s = Arima(Walmart.Close.sqrt, order = c(0,1,0), include.drift = TRUE, seasonal = list(order=c(0,0,1)))

```


#lets make interactive Plots for the test data

```{r}
fWalmart.Close.arima = forecast(Walmart.Close.arima, h=24)
fWalmart.Close.arima.s = forecast(Walmart.Close.arima.s, h=24)
fWalmart.Close.log.arima = forecast(Walmart.Close.log.arima, h=24)
fWalmart.Close.log.arima.s = forecast(Walmart.Close.log.arima.s, h=24)
fWalmart.Close.sqrt.arima = forecast(Walmart.Close.sqrt.arima, h=24)
fWalmart.Close.sqrt.arima.s = forecast(Walmart.Close.sqrt.arima.s, h=24)
```

#lets find RMS error on test set

```{r}
#Values to be predicted
original_val <- window(Walmart.close, start =2018)
rmserr <- function(x,y){
  p =x-y
  r=sum(p^2)
  r = r /length(x)
  r= sqrt(r)
  return (r)
}
(EWalmart.Close.arima <- rmserr(fWalmart.Close.arima$mean,original_val ))
(EWalmart.Close.arima.s <- rmserr(fWalmart.Close.arima.s$mean,original_val))
(EWalmart.Close.log.arima. <- rmserr(exp(fWalmart.Close.log.arima$mean),original_val ))
(EWalmart.Close.log.arima.s <- rmserr(exp(fWalmart.Close.log.arima.s$mean),original_val))
(EWalmart.Close.sqrt.arima. <- rmserr((fWalmart.Close.sqrt.arima$mean)^2,original_val ))
(EWalmart.Close.sqrt.arima.s <- rmserr((fWalmart.Close.sqrt.arima.s$mean)^2,original_val))

```

```{r}

```


#lets see the parameters for the best model
```{r}
Walmart.Close.log.arima.s
```

```{r}
fWalmart.Close.log.arima.s$mean <- 2.718^fWalmart.Close.log.arima.s$mean
fWalmart.Close.log.arima.s$lower <- 2.718^fWalmart.Close.log.arima.s$lower
fWalmart.Close.log.arima.s$upper <- 2.718^fWalmart.Close.log.arima.s$upper
fWalmart.Close.log.arima.s$x <- 2.718^fWalmart.Close.log.arima.s$x
fWalmart.Close.log.arima.s$fitted <- 2.718^fWalmart.Close.log.arima.s$fitted

test_forecast(forecast.obj = fWalmart.Close.log.arima.s, actual = Walmart.close, test = Walmart.Close.test, Xgrid = TRUE, Ygrid = TRUE) %>%
  plotly::layout(legend = list(x = 0.1, y = 0.95), 
                 title = "Comparision of Predicted and Actual Closing Value of 2018 and 19",
                 yaxis = list(linecolor = "rgb(67,67,67)"),
                 xaxis = list(linecolor = "rgb(67,67,67)"))
```

#fitting the best model for time series till 2020 and prediction for 2023
```{r}
Walmart.close.log = log(Walmart.close)
Walmart.close.log.arima.s = Arima(Walmart.close.log, order = c(0,1,0), include.drift = TRUE, seasonal = list(order=c(0,0,1)))
FWalmart.close.log.arima.s = forecast(Walmart.close.log.arima.s,h=36)
exp(Walmart.close.log.arima.s$fitted)
```
```{r}
exp(FWalmart.close.log.arima.s$mean)
exp(FWalmart.close.log.arima.s$lower)
exp(FWalmart.close.log.arima.s$upper)
exp(FWalmart.close.log.arima.s$fitted)
```
```{r}
# Forcasting the Data
FWalmart.close.log.arima.s$mean <- 2.718^FWalmart.close.log.arima.s$mean
FWalmart.close.log.arima.s$lower <- 2.718^FWalmart.close.log.arima.s$lower
FWalmart.close.log.arima.s$upper <- 2.718^FWalmart.close.log.arima.s$upper
FWalmart.close.log.arima.s$x <- 2.718^FWalmart.close.log.arima.s$x
FWalmart.close.log.arima.s$fitted <- 2.718^FWalmart.close.log.arima.s$fitted

plot_forecast(FWalmart.close.log.arima.s, title = "Forcasting of Walmart Share Closing price for 2020 to 2023", Xtitle = "Year", Ytitle = "Closing Stock Price")

#%>% 
#  plotly::layout(legend = list(x = 0.1, y = 0.95),
 #                margin=list(l=20, r=20, t=20, b=20),
  #               yaxis = list(linecolor = "rgb(67,67,67)"),
   #              xaxis = list(linecolor = "rgb(67,67,67)"))


```
```{r}
# Validation of the model by the ljung test 

Box.test(FWalmart.close.log.arima.s$residuals, lag =12, type = "Ljung")


```
```{r}
# Confedence interval ofthe 

confint(Walmart.close.log.arima.s)
FWalmart.close.log.arima.s$mean 

```
#
```{r}
ggtsdiag(Walmart.close.log.arima.s)

```
